Monte Carlo and bootstrap for all parameters with a grid

### 2024-09-12 Intermediary_steps/All3_tables_grid_algo6.Rmd
Better organized

```{r}
# Function to sample at random following the grid
# Algorithm 6 in the report (2024/10/02 version)
sampling_grid1 <- function(i, c_dim){
  # i = 1,...,10
  cells_x <- c()
  cells_y <- c()
  raw <- c()
  elt <- (i-1)*10
  while (elt < (100*1000)) {
    raw <- append(raw, elt)
    elt <- elt+100
  }
  for (j in raw) {
    cells_x <- append(cells_x, ifelse(j%%1000 == 0, 1000, j%%1000))
    cells_y <- append(cells_y, ifelse(j%%1000 == 0, ((j-(j%%1000))/1000) - 1, (j-(j%%1000))/1000) )
  }
  cells_y <- cells_y*10
  a <- mapply(function(x){runif(1, x, x+10)}, cells_x)
  b <- mapply(function(x){runif(1, x, x+10)}, cells_y)
  return(data.frame(x = a, y = b))
}
```

```{r}
# Function to sample at random following the grid
# Algorithm 7 in the report (2024/10/02 version)
sampling_grid2 <- function(i,c_dim){
  # i = 1,...,10
  i <- i-1
random_points <- data.frame(x = numeric(), y = numeric())

@@

>>>>

```{r}
# Function to sample at random following the grid
# Algorithm 6 in the report (2024/10/02 version)
sampling_grid1 <- function(i, c_dim){
  cells_x <- c()
  cells_y <- c()
  raw <- c()
  elt <- i
  while (elt < (1000*1000)) {
    raw <- append(raw, elt)
    elt <- elt+10
  }
  for (j in raw) {
    cells_x <- append(cells_x, ifelse(j%%23 == 0, 23, j%%23))
    cells_y <- append(cells_y, ifelse(j%%23 == 0, ((j-(j%%23))/23) - 1, (j-(j%%23))/23) )
  }
  return(data.frame(x = cells_x, y = cells_y))
}
```

```{r}
# Function to sample at random following the grid
# Algorithm 7 in the report (2024/10/02 version)
sampling_grid2 <- function(i,c_dim){
random_points <- data.frame(x = numeric(), y = numeric())

@@

# Example: Algorithm 6 with stratified bootstrap

res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
# Just one circle to begin with

```{r RS_algo6_strat}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
```

```{r CI_tot_algo6_strat}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
```

```{r CI_ratio_algo6_strat}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

```{r RB_algo6_strat}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

### 2024-09-12 Intermediary_steps/Boot_grid_bis.Rmd
Better organized

---
title: "Monte Carlo and bootstrap for all parameters with a grid"
output: pdf_document
date: "2024-08-01"
---

@@

Motivation: specific sampling from a grid, random small square inside a first bunch of 10 small squares, for a beginning. Then, systematic sampling without any shifts when changing line.

@@

```{r}
i <- sample(1:10, 1) # choice of the rank of the identifier we want
i
```

@@

```{r}
# Function to sample at random following the grid
sampling_grid <- function(i,c_dim){
random_points <- data.frame(x = numeric(), y = numeric())

for (l in 0:((1000/c_dim)-1)) {
  x_init <- i*c_dim
  k <- 0
  while (x_init + 10*c_dim*k < 1000) {
    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
    b <- runif(1, l*c_dim, (l+1)*c_dim)
    random_points <- rbind(random_points, list(a,b))
    k <- k+1
  }
}
colnames(random_points) <- list("x", "y")
return(random_points)
}
```

```{r}
# Small example
ex_grid <- sampling_grid(i, c_dim)
```

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    df_grid <- sampling_grid(i, c_dim)
    a1 <- df_grid$x
    a2 <- df_grid$y
    # n <- nrow(df_grid) # sample size
    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
    var <- mapply(circle_all, a1, a2)
    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))

>>>>

---
title: "Monte Carlo and bootstrap for all parameters with a grid"
output: pdf_document
date: "2024-07-26"
---

@@

Motivation: specific sampling from a grid, random small square inside a bunch of 10 small squares, for each bunch of 10 small squares

@@

```{r}
# i <- sample(1:10, 1) # choice of the rank of the identifier we want
# i
```

@@

```{r}
# Function to sample at random following the grid
sampling_grid <- function(c_dim){
random_points <- data.frame(x = numeric(), y = numeric())

for (l in 0:((1000/c_dim)-1)) { # For all lines
  for (bunch in 1:(1000/(c_dim*10))) { # 10 is the size of each bunch
    x_sampled <- sample(0:9, 1)*c_dim + (bunch-1)*10*c_dim
    a <- runif(1, x_sampled, x_sampled + c_dim)
    b <- runif(1, l*c_dim, (l+1)*c_dim)
    random_points <- rbind(random_points, list(a,b))
  }
}
colnames(random_points) <- list("x", "y")
return(random_points)
}
```

```{r}
# Small example
ex_grid <- sampling_grid(c_dim)
```

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    df_grid <- sampling_grid(c_dim)
    a1 <- df_grid$x
    a2 <- df_grid$y
    # n <- nrow(df_grid) # sample size
    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
    var <- mapply(circle_all, a1, a2)
    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))

### 2024-09-12 Intermediary_steps/Comparison_test.Rmd
Better organized

---
title: "Monte Carlo and bootstrap for all parameters with a grid"
output: pdf_document
date: "2024-07-26"
---

@@

Motivation: specific sampling from a grid, random small square inside a bunch of 10 small squares, for each bunch of 10 small squares

The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees) and variances of these estimators. The same elements, along with confidence intervals, are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations. By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.
We reuse the results from another file for the function that exploits Monte Carlo alone.

In this document, one single circle with a radius of 5 is used to compute local variables. Besides, and more importantly, a grid is used for sampling.

@@

```{r}
# Sample size
n <- 1000
```

```{r}
# i <- sample(1:10, 1) # choice of the rank of the identifier we want
# i
```

```{r}
# Dimension of a small square (length of one side of the square)
# We assume that c_dim is a divisor of 1000
c_dim <- 10
```

```{r}
# Function to sample at random following the grid
sampling_grid <- function(c_dim){
random_points <- data.frame(x = numeric(), y = numeric())

for (l in 0:((1000/c_dim)-1)) { # For all lines
  for (bunch in 1:(1000/(c_dim*10))) { # 10 is the size of each bunch
    x_sampled <- sample(0:9, 1)*c_dim + (bunch-1)*10*c_dim
    a <- runif(1, x_sampled, x_sampled + c_dim)
    b <- runif(1, l*c_dim, (l+1)*c_dim)
    random_points <- rbind(random_points, list(a,b))
  }
}
colnames(random_points) <- list("x", "y")
return(random_points)
}
```

```{r}
# Small example
ex_grid <- sampling_grid(c_dim)
```

```{r}
plot(ex_grid, xlab="", ylab="", main = "Random points within the grid", las = 1)
```

```{r}
plot(ex_grid, xlab="", ylab="", main = "Only one point", xlim = c(0, 100), ylim = c(0, 10), las = 1)
```

```{r}
# True values
cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
```

# Bootstrap for each Monte Carlo iteration

1 000 Monte Carlo iterations and 400 bootstrap iterations for each one are appropriated.

```{r}
f_boot <- function(df_sample, B){
  # df_sample: original sample; 
  # B: number of bootstrap samples made thanks to df_sample

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
    # (n-1) points at random
    sample_b <- df_sample[nb,]
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
}
```

```{r}
# Making of estimations for each sample made by the bootstrap method
est_boot <- function(df, p){
  # df: dataframe with 4*B columns and n rows

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/4 # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + (4*(c-1))]/p))
    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,4*c]/p))/((n/(n-1))*sum(df[,3 + (4*(c-1))]/p)))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(vec_est)
  # Data frame with 3 estimations for each sample
}
```

```{r}
### Function to automate Monte Carlo + bootstrap method

MC_boot <- function(n, B1, B2){
  # B1: number of iterations for MC;
  # B2: number of iterations for bootstrap

  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    df_grid <- sampling_grid(c_dim)
    a1 <- df_grid$x
    a2 <- df_grid$y
    # n <- nrow(df_grid) # sample size
    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
    var <- mapply(circle_all, a1, a2)
    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))

    # Bootstrap iterations
    df_boot <- f_boot(df_b, B2)
    est_boot_val <- est_boot(df_boot, p)

    BOOT_var[[b]] <- list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))

    # Confidence intervals
    norm_CI <- data.frame(useless = rep(0, 2))
    perc_CI <- data.frame(useless = rep(0, 2))
    rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:3) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l,]*2 - lim_sup, est_b[l,]*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l,]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l,]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    norm_CI$useless <- NULL
    perc_CI$useless <- NULL
    rev_perc_CI$useless <- NULL
    colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
    # BOOT_CI <- c(BOOT_CI, CI_b = all_CI)
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste("CI", b, sep = "")
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```

# Example

## Monte Carlo and bootstrap

@@

res2 <- MC_boot(n, B1 = 1000, B2 = 400)
# Just one circle to begin with

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
EST_nb <- c()
EST_vol <- c()
EST_ratio <- c()
for (elt in res2$Estimations) {
  if ("data.frame" %in% class(elt)){ # we target bootstrap samples made from each MC iteration
    EST_nb <- append(EST_nb, mean(elt$est_nb))
    EST_vol <- append(EST_vol, mean(elt$est_vol))
    EST_ratio <- append(EST_ratio, mean(elt$est_ratio))
  }
}
```

```{r}
cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(EST_nb), "\n - for the volume of trees:", mean(EST_vol), "\n - for the ratio volume / number of trees:", mean(EST_ratio))
```

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
VAR_nb <- c()
VAR_vol <- c()
VAR_ratio <- c()
for (elt in res2$Variances) {
  VAR_nb <- append(VAR_nb, elt$var_nb)
  VAR_vol <- append(VAR_vol, elt$var_vol)
  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
}
```

```{r}
cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(VAR_nb), "\n - for the volume of trees:", mean(VAR_vol), "\n - for the ratio volume / number of trees:", mean(VAR_ratio))
```

## Comparison of the variances

```{r}
diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(240516.7, mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(14084.96, mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(6.397115e-06, mean(VAR_ratio)), "%", sep = "")
```

>>>>

---
title: "Comparison_test"
output: pdf_document
date: "2024-08-08"
---

@@

@@

```{r}
# Sample size
n <- 1000
a1 <- runif(n, 0, 1000)
a2 <- runif(n, 0, 1000)
```

# Comparison

@@

var1 <- mapply(circle_all, a1, a2)

@@

var3 <- mapply(circle_ALL_bis, a1, a2)

var5 <- mapply(circle_ALL_quater, a1, a2)

var2 <- mapply(circle_ALL, a1, a2)

### 2024-09-12 Intermediary_steps/MC3_all_old.Rmd
Better organized

---
title: "Monte Carlo and bootstrap for all parameters"
output: pdf_document
date: "2024-07-26"
---

@@

In this document, one single circle with a radius of 5 is used to compute local variables.

@@

res1 <- MonteCarlo(n, 10000)
# Just one circle to begin with

@@

res2 <- MC_boot(n, B1 = 1000, B2 = 400)
# Just one circle to begin with

>>>>

---
title: "Monte Carlo and bootstrap for all parameters with 3 circles"
output: pdf_document
date: "2024-07-26"
---

@@

In this document, three circles are used to compute local variables, like the French NFI process.

@@

res1 <- MonteCarlo(n, 10000)
# With 3 circles

@@

res2 <- MC_boot(n, B1 = 1000, B2 = 400)
# With 3 circles

### 2024-09-12 Intermediary_steps/MC_adagrid_2.Rmd
Better organized

---
title: "Testing bootstrap processes"
output: pdf_document
date: "2024-07-30"
---

@@

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-10))
  for (b in 1:B) {
    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
    # (H-1) strata at random
    sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
    for (number in unique(df_sample[,3])){
      truc <- sample(df_sample[df_sample[,3] == number,], nrow(df_sample[df_sample[,3] == number,]) -1, replace = TRUE)
      sample_b <- rbind(sample_b, truc)
      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
    }
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*5+1 + 1):(b*5+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""), paste("ech", b, colnames(df_sample)[5], sep = ""))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 5)
}
```

@@

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/5 # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (900/899)*sum(df[,4 + (5*(c-1))]/p))
    vec_est2 <- append(vec_est2, (900/899)*sum(df[,5*c]/p))
    vec_est3 <- append(vec_est3, ((900/899)*sum(df[,5*c]/p))/((900/899)*sum(df[,4 + (5*(c-1))]/p)))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(vec_est)
  # Data frame with 3 estimations for each sample
}
```

>>>>

---
title: "Another stratification"
output: pdf_document
date: "2024-07-29"
---

@@

  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-10))
  for (b in 1:B) {
    nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
    # (H-1) strata at random
    sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
    for (number in nb){
      sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
    }
    df_boot <- cbind(df_boot, sample_b)
    colnames(df_boot)[((b-1)*5+1 + 1):(b*5+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""), paste("ech", b, colnames(df_sample)[5], sep = ""))
  }
  df_boot$useless <- NULL
  return(df_boot)
  # Return a data frame with B samples of as many variables as we want (in this application, 5)
}
```

@@

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/5 # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,4 + (5*(c-1))]/p))
    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,5*c]/p))
    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,5*c]/p))/((n/(n-1))*sum(df[,4 + (5*(c-1))]/p)))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(vec_est)
  # Data frame with 3 estimations for each sample
}
```

### 2024-09-12 Intermediary_steps/MC_all.Rmd
Better organized

```{r}
coverage_rate <- function(k){
  CI_nb <- data.frame(useless = c(0,0))
  CI_vol <- data.frame(useless = c(0,0))
  CI_ratio <- data.frame(useless = c(0,0))
  for (elt in res2$`Confidence Intervals`) {
    CI_nb <- cbind(CI_nb, c(unlist(elt[k])[1], unlist(elt[k])[2]))
    CI_vol <- cbind(CI_vol, c(unlist(elt[k])[3], unlist(elt[k])[4]))
    CI_ratio <- cbind(CI_ratio, c(unlist(elt[k])[5], unlist(elt[k])[6]))
  }
  CI_nb$useless <- NULL
  # rownames(CI_nb) <- 1:(nrow(CI_nb))
  # colnames(CI_nb) <- c("x", "y")
  CI_vol$useless <- NULL
  CI_ratio$useless <- NULL

>>>>

```{r}
coverage_rate <- function(k){
  CI_nb <- data.frame(useless = c(0,0))
  CI_vol <- data.frame(useless = c(0,0))
  CI_ratio <- data.frame(useless = c(0,0))
  for (elt in res2$`Confidence Intervals`) {
    CI_nb <- cbind(CI_nb, c(unlist(elt[k])[1], unlist(elt[k])[2]))
    CI_vol <- cbind(CI_vol, c(unlist(elt[k])[3], unlist(elt[k])[4]))
    CI_ratio <- cbind(CI_ratio, c(unlist(elt[k])[5], unlist(elt[k])[6]))
  }
  CI_nb$useless <- NULL
  CI_vol$useless <- NULL
  CI_ratio$useless <- NULL

### 2024-09-12 Intermediary_steps/MC_boot.Rmd
Better organized

>>>>

# A second possibility

Stop calculating the local variable for each bootstrap sample: it is already done with the initial sample!!!

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot1 <- function(df, p){
  # df: dataframe with 3*B columns and n rows

  nboot <- length(df)/3
  vec_est <- c()
  for (c in 1:nboot) {
    vec_est <- append(vec_est, sum(df[,3*c]/p))
  }
  vec_est <- sort(vec_est)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

  for (b in 2:B1) {
    # One MC iteration at a time
    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
    random_points$var <- mapply(f, random_points[, 1], random_points[, 2])
    a <- sum(random_points$var/p)
    est_MC <- append(est_MC, a)

    # Bootstrap iterations
    df_boot <- f_boot(random_points, B2)
    est_boot_val <- est_boot1(df_boot, p)
    mean_est_boot <- append(mean_est_boot, mean(est_boot_val))
    var_est_boot <- append(var_est_boot, var(est_boot_val))
  }
  return(c(mean(est_MC), var(est_MC), mean(var_est_boot)))
  # Estimated value of the total, Monte-Carlo variance, mean of the bootstrap variance
}
```

### 2024-09-12 Intermediary_steps/MC_grid.Rmd
Better organized

---
title: "Monte Carlo and bootstrap for all parameters"
output: pdf_document
date: "2024-08-02"
---

@@

In this document, \textbf{uniform sampling} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.

@@

  for (b in 1:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    # Variables of interest derived from the sample
    var <- mapply(circle_all, a1, a2)
    MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
    MC_df <- cbind(MC_df, MC_b)
    colnames(MC_df)[(4*(b-1)+2):(4*(b-1)+2+3)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
    MC_est <- cbind(MC_est, est_b)
    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
  }
  MC_df$useless <- NULL
  MC_est$useless <- NULL
  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    var <- mapply(circle_all, a1, a2)
    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))

@@

# Example:
## Monte Carlo means of estimations:
##  - for the number of trees: 29251.69
##  - for the volume of trees: 5407.967
##  - for the ratio volume / number of trees: 0.184873
```

@@

# Example:
## Monte Carlo variances:
##  - for the number of trees: 2604340
##  - for the volume of trees: 99936.6
##  - for the ratio volume / number of trees: 1.122037e-05
```

@@

# Example:
## Mean of the means of estimations obtained through each bootstrap process:
##  - for the number of trees: 29280.52
##  - for the volume of trees: 5411.916
##  - for the ratio volume / number of trees: 0.1848212
```

@@

# Example:
## Mean of the variance of bootstrap samples:
##  - for the number of trees: 2562574
##  - for the volume of trees: 98333.62
##  - for the ratio volume / number of trees: 1.121868e-05
```

@@

# Example:
## Difference between the two estimations of variance:
##  - for the number of trees: 1.629866%
##  - for the volume of trees: 1.630143%
##  - for the ratio volume / number of trees: 0.01505727%
```

>>>>

---
title: "Monte Carlo and bootstrap for all parameters with a grid"
output: pdf_document
date: "2024-08-02"
---

@@

In this document, \textbf{sampling with a grid} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.

@@

  for (b in 1:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    df_grid <- sampling_grid(i,c_dim)
    a1 <- df_grid$x
    a2 <- df_grid$y
    # Variables of interest derived from the sample
    var <- mapply(circle_all, a1, a2)
    MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
    MC_df <- cbind(MC_df, MC_b)
    colnames(MC_df)[(4*(b-1)+2):(4*(b-1)+2+3)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
    MC_est <- cbind(MC_est, est_b)
    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
  }
  MC_df$useless <- NULL
  MC_est$useless <- NULL
  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    df_grid <- sampling_grid(i,c_dim)
    a1 <- df_grid$x
    a2 <- df_grid$y
    var <- mapply(circle_all, a1, a2)
    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))

@@

# Example:
## Monte Carlo means of estimations:
##  - for the number of trees: 29529.27
##  - for the volume of trees: 5428.676
##  - for the ratio volume / number of trees: 0.1838376
```

@@

# Example:
## Monte Carlo variances:
##  - for the number of trees: 263478.6
##  - for the volume of trees: 15475.27
##  - for the ratio volume / number of trees: 6.470082e-06
```

@@

# Example:
## Mean of the means of estimations obtained through each bootstrap process:
##  - for the number of trees: 29546.03
##  - for the volume of trees: 5431.112
##  - for the ratio volume / number of trees: 0.1838134
```

@@

# Example:
## Mean of the variance of bootstrap samples:
##  - for the number of trees: 2630037
##  - for the volume of trees: 99634.96
##  - for the ratio volume / number of trees: 1.033748e-05
```

@@

# Example:
## Difference between the two estimations of variance:
##  - for the number of trees: 898.1975%
##  - for the volume of trees: 543.8335%
##  - for the ratio volume / number of trees: 59.77348%
```
